---
title: "**Accessibility Training Discovery Activity**"
subtitle: "Findings, suggestions, and next steps"
logo: images/astho1.png
format: 
  revealjs:
    theme: [default, styles.scss]
    hash-type: number
    controls: auto
    auto-animate-easing: ease-in-out
    auto-animate-unmatched: false
    auto-animate-duration: 0.8
    width: 1260
    height: 750
execute:
  echo: false
  warning: false
  message: false
---

```{r}

source("viz.R")

```

##  {#topics data-menu-title="Topics"}

[**Training Findings** \| Topics]{.slide-header}

<br> <br> <br>

```{r}

topic_bubble
```

##  {#training-modes data-menu-title="Modes"}

[**Training Findings** \| Modes]{.slide-header} <br>

```{r}
mode_cloud
```

##  {#resource-needs data-menu-title="Resources"}

[**Training Findings** \| Resources]{.slide-header} <br>

```{r}
resources_cloud
```

##  {#takeaways data-menu-title="Takeaways"}

[**Training Findings** \| Takeaways]{.slide-header}

<br><br>

::: columns
::: {.column width="30%"}
::: {.fragment .rounded-box style="border: 5px solid #70C4E8; height: 150px;"}
**Who:** <br> <br> All ASTHO Staff
:::

<br>

::: {.fragment .rounded-box style="border: 5px solid #C65227;height: 250px;"}
**What:** <br> <br> Training provided by individuals with disabilities/lived experiences <br> Sharing access stories anonymously <br> External evaluation and reflection
:::
:::

::: {.column width="30%"}
::: {.fragment .rounded-box style="border: 5px solid #EBB41F; height: 150px;"}
**Why:** <br> <br> To integrate accessibility into the fabric of ASTHO for all internal and external processes, etc.
:::

<br>

::: {.fragment .rounded-box style="border: 5px solid #47ba83;height: 250px;"}
**When:**<br> <br> Onboarding <br> All Staff Meetings <br> ASTHO Day/Week <br> Small group sessions within units <br> Other ongoing regularly scheduled meetings
:::
:::

::: {.column width="30%"}
::: {.fragment .rounded-box style="height: 150px; border: 5px solid #c65227;"}
**Where:** <br> Internal platforms (e.g., Break Room/my.ASTHO, monday.com) to reinforce learning and access resources <br> Handbook <br> CD & other ASTHO processes
:::

<br>

::: {.fragment .rounded-box style="height: 250px;"}
**How:** <br> Multimodal learning to cater to different learning needs <br> Gamification and interactive elements to make learning engaging (e.g., Kahoot) <br> Hands-on/interactive sessions <br> Videos and quizzes for self-paced learning <br> Practice evaluations (e.g., evaluating simple sites for accessibility issues)
:::
:::
:::

##  {#suggestions data-menu-title="Key Suggestions"}

[**Training Findings** \| Key Suggestions]{.slide-header}

<br> <br>

::: fragment
**Integration and Regularity:**
:::

::: fragment
Integrate accessibility training into regular training and organizational processes.
:::

::: fragment
Ensure training is ongoing and not just a one-time event.
:::

<br>

::: fragment
**Engagement and Authenticity:**
:::

::: fragment
Incorporate gamification and interactive elements to make learning engaging and accessible.
:::

::: fragment
Amplify voices of those with lived experience via story sharing, hiring disabled trainers, etc.
:::



# Now what? {#discuss data-menu-title="Now what?"}

::: {.fragment style="position: absolute; bottom: 350 px; left: 550px; font-size: 2em;"}
 *Let's discuss!*
:::
